### 2020-07-04 chapters/abstract.tex
Changed images

%Approach/Solution and %Main contributions
In this thesis, we design a method that makes use of lightweight streaming aggregations and distribution divergence functions to alert deviations in data patterns in real-time, while in the presence of large volumes of high velocity, highly skewed and seasonal data. We develop a two-phased and two-windowed method: first we perform a batch analysis on a reference window and then a stream analysis over a sliding streaming window. We aggregate the contents of both windows using an approximate histogram aggregation based on Exponential Moving Averages. We do this for each event and for each of its fields, also denominated features in our context. We measure the divergence between both reference and sliding window histograms for each feature with the Jensen–Shannon Divergence function, but other functions like the Wassertein distance could be used. For each feature, we find out the probability value of each divergence measure and apply the Holm-Bonferroni multiple test correction to find out which probability values are lowest and the associated features. We generate alerts based on a user-defined probability threshold, for each feature.

We evaluate our method through a series of tests, some with synthetic datasets and some with real data. We further split the tests into single and multi feature analysis. Our method accurately detected the introduced anomalies in the synthetic dataset experiments while maintaining high throughput, for single and multi feature analysis. Experiments with real data were not as accurate. Despite not knowing the specific reasons for that, we defer further investigation to future work and formulate a set of hypothesis that might explain it and hence are worthy of pursuing next.

Our set of experiments supports the claim that sliding window aggregations and distribution divergence methods can be combined to detect data pattern shifts in streaming scenarios with constant time and memory complexity.

>>>>

%Approach/Solution and %Main contributions
In this thesis, we design a method that makes use of lightweight streaming aggregations and distribution divergence functions to alert deviations in data patterns in real-time, while in the presence of large volumes of high velocity, highly skewed and seasonal data. We develop a two-phased and two-windowed method: first we perform a batch analysis on a reference window and then a stream analysis over a sliding streaming window. We aggregate the contents of both windows using an approximate histogram aggregation based on Exponential Moving Averages. We do this for each event and for each of its fields, also denominated features in our context. We measure the divergence between both reference and sliding window histograms for each feature with the Jensen–Shannon Divergence function, but other distance functions could be used. For each feature, we find out the probability value of each divergence measure and apply the Holm-Bonferroni multiple test correction to find out which probability values are lowest and the associated features. We generate alerts based on a user-defined probability threshold, for each feature.

We evaluate our method through a series of tests, some with synthetic datasets and some with real data. We further split the tests into single and multi feature analysis. Our method accurately detected the introduced anomalies in the synthetic dataset experiments while maintaining high throughput, for single and multi feature analysis. However, experiments with real data were not as accurate. Despite not knowing the specific reasons for that, we defer further investigation to future work and formulate a set of hypothesis that might explain it and hence are worthy of pursuing next.

Our set of experiments supports the claim that sliding window aggregations and distribution divergence methods can be combined to detect data pattern shifts in streaming scenarios with constant time and memory complexity regarding window size.
